### 2020-06-17 magic_paper.tex
Composition condition for resource projection definitions needs more discussion

Monotones reduce the structure of the resource theory $\R$ to a \emph{total} order on the real numbers.
Therefore, two states, even if incomparable in $\R$, are always mapped onto ordered real numbers.
We now generalise this idea to any projection of the theory that ensures a form of comparison between states.
\begin{definition}[\textbf{Covariant projection}]\label{def:covproj}
Let $\R = (\F, \O)$ be a resource theory with pre-order $\prec_\R$. 
Then a \emph{covariant resource projection} of $\R$ into a resource theory $\R'$ with pre-order $\prec_{\R'}$, is a pair of mappings $(\Pi_s, \Pi_o)$, where $\Pi_s$ maps quantum states in $\R$ into quantum states in $\R'$, and $\Pi_o$ maps free operations in $\R$ into free operations in $\R'$. 
Moreover, these obey
	\begin{enumerate}
        \item $\Pis(\rho_2) \prec_{\R'} \Pis(\rho_1)$ whenever $\rho_1 \prec_\R \rho_2$;
        \item $\Pio(\E) = \Pio(\E_1) \circ \Pio(\E_2)$ whenever $\E = \E_1 \circ \E_2$.
    \end{enumerate}
We call $\R'$ a \emph{covariant fragment} of $\R$.
\end{definition}

Resource monotones can now be clearly seen as covariant projections of resource theories.
\begin{proposition}\label{thm:monoproj}
	Let $\M$ be a resource monotone of a resource theory $\R$. 
	Then $\M$ is a covariant projection that reduces the pre-order $\prec_\R$ to a total order.
\end{proposition}
\begin{proof}
	Consider a monotone $\M$ in the context of a general resource theory $\R = (\F, \O)$.
	The defining property of a monotone, stated in~\cref{def:mono} ensures order preservation under state projection $\Pis$.	
	Let $\Pio$ project any $\E \in \O$ onto a real non-increasing function $f$ mapping $\M(\rho)$ to $\M(\E(\rho))$ for all states $\rho$.
	Then, the composition of functions is preserved under operation projection $\Pio$.	
	The ordered pair $(\Pis, \Pio)$ is the covariant resource projection which corresponds to monotone $\M$.
\end{proof}

On the other hand, $\sigma$--fragments are an example of reducing the structure of a magic theory $\R$ to a subtheory with a tractable pre-order.
States which are incomparable in $\R$ remain incomparable, but transformations between comparable states may no longer be possible.
We generalise the idea of reducing the structure of a theory into a simpler one, by introducing two types of resource projections.
\begin{definition}[\textbf{Contravariant projection}]\label{def:contraproj}
	Let $\R = (\F, \O)$ be a resource theory with pre-order $\prec_\R$. 
Then a \emph{contravariant resource projection} of $\R$ onto a resource theory $\R'$ with pre-order $\prec_{\R'}$, is a pair of mappings $(\Pi_s, \Pi_o)$, where $\Pi_s$ maps quantum states in $\R$ onto quantum states in $\R'$, and $\Pi_o$ maps free operations in $\R$ onto free operations in $\R'$. 
Moreover, these obey
	\begin{enumerate}
        \item $\rho_1 \prec_\R \rho_2$ whenever $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$;
        \item $\E = \E_1 \circ \E_2$ whenever $\Pio(\E) = \Pio(\E_1) \circ \Pio(\E_2)$.
    \end{enumerate}
We call $\R'$ a \emph{contravariant fragment} of $\R$.
\end{definition}
The use of covariant and contravariant in~\cref{def:covproj,def:contraproj} refers to the direction of implication between the two pre-orders and operation compositions\footnote{Note that strictly these are not projections in the sense of $\Pi^2 = \Pi$, but are instead morphisms. 
Here our use of the term projection is motivated by the idea that one one generally loses information about $\R$ under the mapping.}.

\begin{proposition}\label{thm:sigmaproj}
    Let $\R = (\F, \O)$ be a theory of magic.
    Every $\sigma$--fragment $(\F, \O_\sigma)$ is a contravariant fragment of $\R$.
\end{proposition}
\begin{proof}
    Let the state projection $\Pis$ map all states onto themselves, so order preservation is trivially satisfied.    
    Consider the operation projection $\Pio:\O \mapsto \O_\sigma$, defined as
    \begin{equation}
    \Pio(\E) =
    \begin{cases}
        \E,\ &\E \in \O_\sigma, \\
        1_{\rm{C}},\ &\E \notin \O_\sigma.
    \end{cases}
    \end{equation}
    Since for any $\E_1, \E_2 \in \O_\sigma,$ it is also true that $\E_1 \circ \E_2 \in \O_\sigma$, operational composition is contravariantly preserved.
\end{proof}

\begin{proposition}
	Let $\R = (\F,\O)$ be a resource theory, and let $\D \in \O$ be a free operation, which is reversible by $\D_{\rm{rev}} \in \O$, so that $\D_{\rm{rev}} \circ \D = 1_{\rm{C}}$.

	Then, we can define a contravariant projection of $\R$, by acting with $\D$ on all states.
\end{proposition}
\begin{proof}
	We show that the theory $\R' = (\F', \O)$, with $\F' = \{\D(\rho):\rho \in \F \}$, is a contravariant fragment of $\R$.
	Let $\Pis$ map every state $\rho$ to $\D(\rho)$.
	Then, $\D(\rho_1) \prec \D(\rho_2)$ implies that there exists $\E \in \O$ such that $\rho_1 = (\D_{\rm{rev}} \circ \E \circ \D) (\rho_2)$, so the state order is preserved contravariantly.

@@

\nick{If $\D$ is a recovery map, so that $\D \circ \D_{\rm{rev}} = 1_{\rm{C}}$, then this is a covariant projection instead.

@@

    Consider the operation projection $\Pio:\O \mapsto \O_\sigma$, defined as
    \begin{equation}
    \Pio(\E) =
    \begin{cases}
        \E,\ &\sigma \in \O, \\
        1_{\rm{C}},\ &\sigma \notin \O.
    \end{cases}
    \end{equation}
    \nick{$\Pio$ should be different, this here is not right. If we need to project every $\E \in \O$, we may need a different condition on $\Pio$ than $\Pio(\E_1) \circ_{\R'} \Pio(\E_2) = \Pio(\E_1 \circ_{\R} \E_2)$.}
    The ordered pair $(\Pis, \Pio)$ acts as the desired projection.
\end{proof}

>>>>

Monotones reduce the structure of the resource theory $\R$ to a \emph{total} order on the real numbers.
Therefore, two states, even if incomparable in $\R$, are always mapped onto ordered real numbers.
We now generalise this idea of a theory projection that preserves comparability between states.
\begin{definition}[\textbf{Covariant projection}]\label{def:covproj}
Let $\R = (\F, \O)$ be a resource theory with pre-order $\prec_\R$. 
Then a \emph{covariant resource projection} of $\R$ into a resource theory $\R'$ with pre-order $\prec_{\R'}$, is a pair of mappings $(\Pi_s, \Pi_o)$, where $\Pi_s$ maps quantum states in $\R$ into quantum states in $\R'$, and $\Pi_o$ maps free operations in $\R$ into free operations in $\R'$. 
Moreover, these obey
	\begin{enumerate}
        \item $\Pis(\rho_2) \prec_{\R'} \Pis(\rho_1)$ whenever $\rho_1 \prec_\R \rho_2$;
        \item $\Pio(\E) = \Pio(\E_1) \circ \Pio(\E_2)$ whenever $\E = \E_1 \circ \E_2$.
    \end{enumerate}
We call $\R'$ a \emph{covariant fragment} of $\R$.
\end{definition}

Resource monotones can now be clearly seen as covariant projections of resource theories.
\begin{proposition}\label{thm:monoproj}
	Let $\M$ be a resource monotone of a resource theory $\R$. 
	Then $\M$ is a covariant projection that reduces the pre-order $\prec_\R$ to a total order.
\end{proposition}
\begin{proof}
	Consider a monotone $\M$ in the context of a general resource theory $\R = (\F, \O)$.
	The defining property of a monotone, seen in~\cref{def:mono} ensures order preservation under state projection $\Pis = \M$, where the pre-order $\prec_{\R'}$ is simply the total order $\leq$ of real numbers.

	Let $\Pio$ project any $\E \in \O$ onto a real non-increasing function $f$ defined by mapping $\M(\rho)$ to $\M(\E(\rho))$ for every state $\rho$.
	Then, composition of free opearations implies composition of their function projections. \nick{expand?}

	The ordered pair $(\Pis, \Pio)$ is the covariant resource projection which corresponds to monotone $\M$.
\end{proof}

On the other hand, $\sigma$--fragments are an example of reducing the structure of a magic theory $\R$ to a subtheory with a tractable pre-order.
States which are incomparable in $\R$ remain incomparable, but conversions between states which are comparable in $\R$ may no longer be possible.
\begin{definition}[\textbf{Contravariant projection}]\label{def:contraproj}
	Let $\R = (\F, \O)$ be a resource theory with pre-order $\prec_\R$. 
Then a \emph{contravariant resource projection} of $\R$ onto a resource theory $\R'$ with pre-order $\prec_{\R'}$, is a pair of mappings $(\Pi_s, \Pi_o)$, where $\Pi_s$ maps quantum states in $\R$ onto quantum states in $\R'$, and $\Pi_o$ maps free operations in $\R$ onto free operations in $\R'$. 
Moreover, these obey
	\begin{enumerate}
        \item $\rho_1 \prec_\R \rho_2$ whenever $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$;
        \item $\E = \E_1 \circ \E_2$ whenever $\Pio(\E) = \Pio(\E_1) \circ \Pio(\E_2)$.
    \end{enumerate}
We call $\R'$ a \emph{contravariant fragment} of $\R$.
\end{definition}
Note that a contravariant projection is always a surjective mapping for both states and operations, so that the conditions in~\cref{def:contraproj} make sense.
The use of covariant and contravariant in~\cref{def:covproj,def:contraproj} refers to the direction of implication between the two pre-orders and operation compositions\footnote{Note that strictly these are not projections in the sense of $\Pi^2 = \Pi$, but are instead morphisms. 
Here our use of the term projection is motivated by the idea that one one generally loses information about $\R$ under the mapping.}.

\begin{proposition}\label{thm:subproj}
    Let $\R = (\F, \O)$ be a general resource theory. 
    Then, any subtheory $\R' = (\F, \O')$ of $\R$, where $\O' \subseteq \O$, is a contravariant fragment of $\R$.    
\end{proposition}
\begin{proof}
    We will establish a contravariant projection $(\Pis, \Pio)$ from $\R$ to $\R'$.
    Let the state projection $\Pis$ map all states onto themselves and suppose that $\rho_1 \prec_{\R'} \rho_2$. 
    Then, there exists $\E \in \O' \subseteq \O$ such that $\rho_1 = \E(\rho_2)$, therefore $\rho_1 \prec_{\R} \rho_2$ as well.

    Consider the operation projection $\Pio:\O \mapsto \O'$, defined as
    \begin{equation}
    \Pio(\E) =
    \begin{cases}
        \E,\ &\E \in \O', \\
        1_{\rm{C}},\ &\E \notin \O',
    \end{cases}
    \end{equation}    
    This projection ensures that operational composition is contravariantly preserved.
    For any $\E_1, \E_2 \in \O'$, then $\E =\E_1 \circ \E_2 \in \O_\sigma$ as well, so $\E = \Pio(\E) = \Pio(\E_1) \circ \Pio(\E_2) = \E_1 \circ \E_2$.
    If $\E_1 \notin \O'$ or $\E_2 \notin \O'$, then $\Pio(\E) \neq \Pio(\E_1) \circ \Pio(\E_2)$.

    \nick{This does not hold in the case of all $\E, \E_1, \E_2 \notin \O'$. We need to update the composition condition in~\cref{def:contraproj}}
\end{proof}
As an immediate corollary of~\cref{thm:subproj}, a $\sigma$--fragment of any magic theory $\R$ is a contravariant fragment of $\R$.

\begin{proposition}
	Let $\R = (\F,\O)$ be a resource theory, and let $\D \in \O$ be a free operation, which is reversible by $\D_{\rm{rev}} \in \O$, so that $\D_{\rm{rev}} \circ \D = \idc$.

	Then, we can define a contravariant projection of $\R$, by acting on all quantum states with $\D$.
\end{proposition}
\begin{proof}
	We show that the theory $\R' = (\F', \O)$, with $\F' = \{\D(\rho):\rho \in \F \}$, is a contravariant fragment of $\R$.

	Let $\Pis$ map every state $\rho$ to $\D(\rho)$ and suppose $\D(\rho_1) \prec \D(\rho_2)$. 
	Then, there exists $\E \in \O$ such that $\rho_1 = (\D_{\rm{rev}} \circ \E \circ \D) (\rho_2)$, so $\rho_1 \prec \rho_2$.

@@

\nick{If $\D$ is a recovery map, so that $\D \circ \D_{\rm{rev}} = \idc$, then this is a covariant projection instead.

@@

    Consider the operation projection $\Pio:\O \mapsto \O_\sigma$, defined as
    \begin{equation}
    \Pio(\E) =
    \begin{cases}
        \E,\ &\sigma \in \O, \\
        \idc,\ &\sigma \notin \O.
    \end{cases}
    \end{equation}
    \nick{$\Pio$ should be different, this here is not right. If we need to project every $\E \in \O$, we may need a different condition on $\Pio$ than $\Pio(\E_1) \circ_{\R'} \Pio(\E_2) = \Pio(\E_1 \circ_{\R} \E_2)$.}
    The ordered pair $(\Pis, \Pio)$ acts as the desired projection.
\end{proof}
